FictionEro - Affective Impact of Fiction

### 2025-09-01 analysis/analysis.qmd
updated analysis

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)

@@

dfsub1 <- dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data_participants.csv")
df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
           BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
           GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
           Screen_Size,
           -Feedback_Comments),
    by = "Participant"
    ) |> 
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
         Sex =  fct_relevel(Sex, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False"
         )) |> 
  mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
```

@@

```{r Arousal1}
#| fig-width: 12
arousal_dist1 <- df1 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.4, colour = "black", bins = 20) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 1", ) +
  facet_wrap(~Sex) +
   scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

@@

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
results_table(arousal1)

pred_a1 <- estimate_means(arousal1, by = c("Sex", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
  as.data.frame()

pred_a1|>
  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |>
  ggplot(aes(x = Arousal, y= Proportion ))

@@

```{r}
arousal2 <- readRDS("models/ModelArousal_2.rds")
results_table(arousal2)

pred_a2 <- estimate_means(arousal2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans") |>
  as.data.frame()
```

@@

>>>>

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)
library(gt)

@@

dfsub1 <- dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data_participants.csv")
df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data.csv") |> 
  right_join(
    select(dfsub1, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
           BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
           GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
           Screen_Size,
           -Feedback_Comments),
    by = "Participant") |> 
  rename(Gender = Sex) |>
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False"
         )) |> 
  mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
```

@@

```{r Arousal1}
#| fig-width: 12
arousal_dist1 <- df1 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.4, colour = "black", bins = 20) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 1", ) +
  facet_wrap(~Gender) +
   scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

tbl_results <-   function(model1,                                         title_table = "Fixed Effects: Study 1"){

  # ---- Fixed effects table ----
  tbl <- parameters::parameters(model1) |>
    as.data.frame() |>
    select(-Effects, -Group, -Component, -df_error, -CI) |>
    gt() |>
    # tab_header(title = title_table, subtitle = subtitle_table) |>
    fmt_number(columns = c("Coefficient", "SE", "CI_low", "CI_high", "z", "p"), decimals = 2) |>
    cols_label(
      Parameter = "Predictor",
      Coefficient = "β",
      SE = "SE",
      CI_low = "CI (lower)",
      CI_high = "CI (upper)",
      z = "z-value",
      p = "p"
    ) |>
    cols_merge(columns = c("CI_low", "CI_high"), pattern = "{1}, {2}") |>
    cols_label(`CI_low` = "95% CI") |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels(everything())
    ) |>
    opt_table_lines()

    return(tbl)
}

```{r}
make_model_plot <- function(model1, model2 = NULL, 
                            title = "Estimated Marginal Means") {

    pred_df <- rbind(
      modelbased::estimate_means(model1, by = c("Gender", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
        filter(Relevance == "Relevant") |>
        select(-Relevance) |>
        mutate(Sample = "Study 1")|>
      as.data.frame(), 
      modelbased::estimate_means(model2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans")|>
        mutate(Sample = "Study 2") |>
        as.data.frame())

    plt <- pred_df |>
      ggplot(aes(x = ConditionBelief,y = Proportion, color = Condition,linetype = Sample, group = interaction(Sample, Condition))) +
      geom_line(size = 1) +
      geom_point(size = 2) +
      geom_errorbar(aes(ymin = CI_low, ymax = CI_high),width = 0.1) +
      facet_wrap(~ Gender) +
      scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
      theme_minimal(base_size = 14) +
        labs(x = "Whether the original labels were believed to be true",y = "Estimated Proportion",color = "Images presented as:",linetype = "Sample", title = "Enticement") +
      theme(
            axis.text.y = element_text(size = 8),
            strip.placement = "outside",
            strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
            strip.text.x = element_text(size = 10),
            strip.text.y = element_text(size = 10),
            axis.text.x = element_text(face = "bold", size=9, color="black"),
            legend.text = element_text(size = 10),
            legend.position =  )

    return(plt)
}

@@

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
arousal2 <- readRDS("models/ModelArousal_2.rds")
```

tbl_a1 <- tbl_results(arousal1, title = "Fixed Effects: Arousal Study 1")
tbl_a2 <- tbl_results(arousal2, title = "Fixed Effects: Arousal Study 2")

@@

plt_a <- make_model_plot(arousal1, arousal2,
                title = "Arousal for Relevant Stimuli")
```

### Enticement

```{r}
enticement1 <- readRDS("models/ModelEnticement_1.rds")
enticement2 <- readRDS("models/ModelEnticement_2.rds")
```

tbl_e1 <- tbl_results(enticement1, title = "Fixed Effects: Enticement Study 1")
tbl_e2 <- tbl_results(enticement2, title = "Fixed Effects: Enticement Study 2")

plt_e <- make_model_plot(enticement1, enticement2,
                title = "Enticement for Relevant Stimuli")
```

### Valence

```{r}
valence1 <- readRDS("models/ModelValence_1.rds")
valence2 <- readRDS("models/ModelValence_2.rds")
```

tbl_v1 <- tbl_results(valence1, title = "Fixed Effects: Valence Study 1")
tbl_v2 <- tbl_results(valence2, title = "Fixed Effects: Valence Study 2")

plt_v <- make_model_plot(valence1, valence2,
                title = "Valence for Relevant Stimuli")
```

@@

1. extract random effects
2. make plot of participant effects
3. effect of condition believed + relevant 
4. correlation matrix/ matrix of scatter plots
